---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE)
```

<br><br>

# R Shiny Apps {.tabset .tabset-fade}

The Shiny apps collected here are broken out into sections based roughly on the age of the apps. The older generations of apps date back to when Shiny was in early alpha status. Including them provides a picture of
the historical development trajectory and all the changes that occurred along the way.

```{r showcase}
library(shiny)
library(apputils)
library(snaputils)
labs <- paste0("<h4>", snapps_titles("label"),
  "<a href=\"", snapps_urls("gh"), "\" style=\"padding-left:10px;\"><span class=\"fa fa-github fa-lg\"></span></a></h4>")
labs <- purrr::map(labs, ~HTML(.x))
```

## Highlighted apps

These apps are selected for the collection's consistent polished look and feel while ranging from small to large and fairly simple to highly complex.

```{r showcase_highlighted}
app_showcase(snapps_urls()[1:6], snapps_urls("img")[1:6], snapps_titles("title")[1:6], snapps_titles("sub")[1:6], labs[1:6])
```

## Older climate apps

These apps and those on subsequent tabs are relatively dated compared to the highlighted apps, but all apps are maintained. The last few apps listed below are some of the earliest app I created, circa early 2013.
Note that the `CMIP3/CMPI5 climate` app is not publicly available, but the code is still viewable on GitHub.

```{r showcase_olderclim}
idx <- c(7:10, 16, 21:23)
app_showcase(snapps_urls()[idx], snapps_urls("img")[idx], snapps_titles("title")[idx], snapps_titles("sub")[idx], labs[idx])
```

## Assorted examples

Example apps here offer a somewhat random assortment of content.
Note that the `ALFRESCO launcher` Shiny app for running SNAP's projected wildfire simulations model is viewable,
but cannot actually be used to run the model online, so the app does not actually do anything here.

```{r showcase_assorted}
idx <- c(14, 11, 13, 12, 24, 15)
app_showcase(snapps_urls()[idx], snapps_urls("img")[idx], snapps_titles("title")[idx], snapps_titles("sub")[idx], labs[idx])
```

## Random variables

The four versions of this app are some of the oldest and were used to demonstrate an app development trajectory of increasing complexity at a time when Shiny was in early development.

```{r showcase_rv}
idx <- 17:20
app_showcase(snapps_urls()[idx], snapps_urls("img")[idx], snapps_titles("title")[idx], snapps_titles("sub")[idx], labs[idx])
```
