---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE)
```

```{r showcase_setup}
library(shiny)
library(apputils)
pkgs <- snapmeta::sv_pkgs()
page_urls <- paste0("http://leonawicz.github.io/", pkgs$pkg)
img_urls <- paste0("assets/img/pkg_icon_", pkgs$pkg, ".svg")
gh_urls <- paste0("https://github.com/leonawicz/", pkgs$pkg)
lab <- paste0("<h4>", pkgs$pkg,
  "<a href=\"", gh_urls, "\" style=\"padding-left:10px;\"><span class=\"fa fa-github fa-lg\"></span></a></h4>")
lab <- purrr::map(lab, ~HTML(.x))
titles <- paste0(pkgs$pkg, ifelse(pkgs$type == "sector", "", " package"))
sv_subtitles <- function(type){
  switch(type, 
         "sector"="Sector package", 
         "functions"="Functions package",
         "data"="Data package",
         "apps"="SNAPlications package",
         "satellite" = "Satellite package")
}
subtitles <- purrr::map_chr(pkgs$type, ~sv_subtitles(.x))
pkg <- pkgs$pkg
```

<br><br>

# SNAPverse R Packages {.tabset .tabset-fade}

## Sector packages

#### Sector packages are convenient for loading several R packages at once.

```{r showcase_sector}
idx <- pkgs$type == "sector"
app_showcase(page_urls[idx], img_urls[idx], pkg[idx], subtitles[idx], lab[idx])
```

The primary sector package is `snapverse`. It does not load every package in the SNAPverse, but it does load all
packages from the functions, data, and web apps and docs sectors of the verse.
`snaplite` loads only functions packages. `snapdata` loads data packages.
`snapwebs` loads packages containing collections of SNAP Shiny apps, dashboards and other interactive documents.

<br><hr><br>

## Analysis

#### Analyze and graph data from the SNAPverse with functions sector packages.

```{r showcase_functions}
idx <- pkgs$type == "functions"
app_showcase(page_urls[idx], img_urls[idx], pkg[idx], subtitles[idx], lab[idx])
```

The package of most use and interest to a general audience working with SNAP data is `snapfuns`.
The other packages, `snapprep` and `alfresco` cater to internal use and do not contain functions useful for
analyzing and graphing data sets from SNAPverse data packages. That is specifically what `snapfuns` exists for.
Users other than the author are safe to ignore the other packages.

<br><hr><br>

## Curated data sets

#### Data sector packages offer curated data sets from the SNAPverse ready for exploration.

```{r showcase_data}
idx <- pkgs$type == "data"
app_showcase(page_urls[idx], img_urls[idx], pkg[idx], subtitles[idx], lab[idx])
```

These data packages offer a range of data sets including spatially explicit maps, vector maps (spatial polygons data frames),
climate data sets, historical observed wildfire data and projected ALFRESCO wildfire simulation model output, and much more.
Any of the data in these packages can be loaded and worked with directly in R in whatever ways an R user wishes to interact with the data.
A convenient and recommended approach, however, is to use functions from the `snapfuns` package to work with these data sets.
`snapfuns` provides a number of R functions that streamline some of the most common operations users perform when analyzing
and graphing SNAPverse data.

<br><hr><br>

## SNAPlications

#### Example apps and interactive documents collected in convenient R packages.

```{r showcase_apps}
idx <- pkgs$type == "apps"
app_showcase(page_urls[idx], img_urls[idx], pkg[idx], subtitles[idx], lab[idx])
```

These packages provide direct, offline access to collections of SNAP Shiny apps, dashboards and more.
Users of SNAPlications may be familiar with the large historical repository of archived R Shiny apps by SNAP as well
other apps associated and packaged with various distinct SNAP projects.

Packages here like `snapapps` collect several SNAP Shiny apps in one place, fully encapsulated inside an R package.
This allows users to launch apps locally after simply installing and loading the package in their R session.
This removes the need for a user to interact directly with apps hosted on [shinyapps.io](http://shinyapps.io/)
and avoids the need to download various repositories from GitHub.
It helps to expose source code for these example apps while providing a convenient and local method for launching 
and exploring the collection of packaged Shiny apps.

One thing to consider is that some apps use a lot of data, enough data that it is not stored in the app.
Rather, the data is sourced externally from somewhere like Amazon Web Services.
In cases like these, a limitation is that these apps are cut down to a tiny subset of the original data
in order to provide a small self-contained example app that is just like the original hosted online, but will not offer
access to all the data of the original app.

<br><hr><br>

## Satellites packages

#### R packages that are related to the SNAPverse but not part of the verse core.

```{r showcase_satellite}
idx <- pkgs$type == "satellite"
app_showcase(page_urls[idx], img_urls[idx], pkg[idx], subtitles[idx], lab[idx])
```

Some satellite packages like `snapmeta` and `snapsite` are used only for development of the SNAPverse itself and are not useful to anyone but the author and SNAPverse maintainer.
These along with others like `snaputils` are also specific to SNAP data and workflows and are not useful outside of a SNAP context.
The remaining satellite packages, however, are useful to a wide audience of R users and are not SNAP-specific at all.
They are only considered satellites to the SNAPverse collection of R packages in that core SNAPverse packages may make thorough use of them
as dependencies.
These include `rvtable`, `apputils` and `maputils`.

<br><hr><br>

# The SNAPverse at a glance

<p style="text-align:center;"><img src="assets/img/sv_all.svg"></p><br>
